---
title: "Workout"
author: "Reigne Dadey"
date: "9 March 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/RD/Documents/R/workout1/")

library("tidyverse")
library("readr")
classes <-
  c(
    "integer", #id
    "factor", #team_name
    "character", #game_date
    "factor", #season
    "integer", #period
    "integer", #minutes_remaining
    "integer", #seconds_remaining
    "character", #shot_made_flag
    "factor", #action_type
    "factor", #shot_type
    "integer", #shot_distance
    "factor", #opponent
    "integer", #x
    "integer", #y
    "character", #names
    "integer" #minutes remaining
  )

players <-
  read_csv(
  "./data/shots.data.csv",
  col_types = cols_only(
  team_name = col_character(),
  game_date = col_character(),
  season = col_double(),
  period = col_double(),
  minutes_remaining = col_double(),
  seconds_remaining = col_double(),
  shot_made_flag = col_character(),
  action_type = col_character(),
  shot_type = col_character(),
  shot_distance = col_double(),
  opponent = col_character(),
  x = col_double(),
  y = col_double(),
  name = col_character(),
  minutes = col_double()
  )
  )
  
```
#What makes basketball greatness?
For California's Golden State Warriors, the 2016 season was another resounding success.  After breaking a forty-year championship drought in 2014-2015, the team won their second of three NBA titles in four years.  But what was the reason for their success?

Many argue that this is in no part, due to the work of the Golden Warrior's five captains:  Andre Iguodala, Stephen Curry, Klay Thompson, Draymond Green and Kevin Durant.  All five players are strong shooters; and all maintained a 40% + success rate for all shots made during the season.  However, there is significant variation in the players' shooting styles, which begs the question:  do the players make the team, or does the team make the players?

To explain the Warrior's resounding success, this article will analyse the shooting patterns of the these captains.

##About the players


```{r generate tables}

twopts <- players %>%
  filter(shot_type == "2PT Field Goal") %>%
  group_by(name) %>%
  summarise(Total = length(shot_type), Made = length(shot_made_flag[shot_made_flag == "shot.yes"]), Percentage = Made*100/Total) %>%
  arrange(desc(Percentage))

threepts <- players %>%
  filter(shot_type == "3PT Field Goal") %>%
  group_by(name) %>%
  summarise(Total = length(shot_type), Made = length(shot_made_flag[shot_made_flag == "shot.yes"]), Percentage = Made*100/Total) %>%
  arrange(desc(Percentage))

allpts <- players %>%
  group_by(name) %>%
  summarise(Total = length(shot_type), Made = length(shot_made_flag[shot_made_flag == "shot.yes"]), Percentage = Made*100/Total) %>%
  arrange(desc(Percentage))

as.data.frame(twopts)
as.data.frame(threepts)
as.data.frame(allpts)

```
