title: "Using Binomial"
author: "Reigne Dadey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T)
library(Binomial)
```

## About the package

The package `"Binomial"` provides a simple binomial probability calculator and graphing tool.


## Basic functions`

The functions bin_mean, bin_median, bin_mode, bin_skewness and bin_kurtosis provide basic descriptive stats:

```{r}
mean <- bin_mean(trials = 10, prob = 0.5)
mode <- bin_mode(trials = 10, prob = 0.5)
kurtosis <- bin_kurtosis(trials = 10, prob = 0.5)
```

By default, the functions do not specify default values.

## Generating tables

The functions bin_distribution, and bin_cumulative, generate PDF and CDF tables respectively.  In addition, bin_probability provides a simple distribution of the binomial variable.

```{r}
pdf <- bin_distribution(trials = 10, prob = 0.5)
cdf <- bin_cumulative(trials = 10, prob = 0.5)
sum <- bin_variable(trials = 10, prob = 0.5)
```


## Plot of relative frequencies

You can use the functions `plot()`and summarise() to create graphs and summary tables which illustrate the likelihood of various outcomes:

```{r, fig.show='hold'}
plot(cdf) #plots CDF function

summary(sum) #shows detailed summary


```
